Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-18 paper.tex
Update introduction

Scaled physical models are often used in science and engineering to approximate
real-world systems. In the fields of wind and marine hydrokinetic (MHK) energy,
scaled physical models are used to validate predictive numerical models, predict
full-scale performance of individual turbines, and design or investigate arrays
of devices. Despite being significantly less expensive, there is still some
concern at which scale an experiment must be performed to be relevant to
full-scale application.

For numerical models, one might obtain favorable predictions for scaled systems
due to modified physics. If the numerical model is then considered
``validated,'' there is a risk that its application at full-scale may produce
incorrect predictions. For scaled physical prototypes, it is of interest how
small---since size, or scale generally correlates inversely with cost---the
prototype can be while remaining a reliable predictor of full-scale behavior.

@@

Previously we took a general look at how maximum performance and some 2-D wake
profiles are affected by Reynolds number, but here we look deeper. In this study
we set out to measure the effects of scale, i.e. Reynolds number on the
performance of the turbine, and its near-wake characteristics. We were looking
to find a threshold scale beyond which a physical model study could reliably
predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.

@@

Turbine performance is strongly dependent on the lift-to-drag ratio $l/d$ acting
on the blades, which is a function of the blades' angles of attack $\alpha$.
These angles of attack are a function of turbine tip speed ratio, induction
(slowing/turning of the free stream flow prior to reaching the turbine), and
turbine rotation or azimuthal angle $\theta$. Looking at static airfoil data, we
see that the static stall angle---the angle just beyond that at which $l/d$ is
maximum, characterized by flow separation near the leading edge---increases with
blade chord Reynolds number $Re_c$. This can be explained as the transition to a
turbulent boundary layer adjacent to the blade delaying separation. However,
static foil performance does not tell the whole story for a cross-flow turbine.
The azimuthal, and therefore temporal variation of $\alpha$ in a cross-flow
turbine implies the occurrence of dynamic stall at tip speed ratios at and below
those of maximum rotor torque\cite{Para2002}. We then must understand the
effects of Reynolds number on the dynamic stall process.

@@

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. However, the principle of dynamic similarity allows for
geometrically scaled systems to be dynamically identical in scale if certain
nondimensional physical parameters are matched. In the case of fluid systems,
the most important parameter is often the Reynolds number, which quantifies the
importance of viscosity on the flow. As such, hereafter we will use the word
``scale'' to refer to this dynamical scale rather than the geometric scale.

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Despite being significantly less expensive, there is still some concern at which
scale an experiment must be performed to be relevant to full-scale application.

For numerical models, one might obtain favorable predictions for scaled systems
due to modified physics. If the numerical model is then considered
``validated,'' there is a risk that its application at full-scale may produce
incorrect predictions. For scaled physical prototypes, it is of interest how
small---since size, or scale generally correlates inversely with cost---the
prototype can be while remaining a reliable predictor of full-scale behavior. At
the very least, it is necessary to test at a scale where results can be
extrapolated, i.e. changes are occurring quasi-linearly without dramatic changes
in the underlying physical principles governing the behavior of interest, e.g.
power production in the case of a wind or MHK turbine.

@@

Bachant and Wosnik observed how maximum performance and 2-D near-wake profiles
are affected by Reynolds number, but here we look deeper. In this study we set
out to measure the effects of scale, i.e. Reynolds number, on the performance of
the turbine, and its more detailed near-wake characteristics. We were looking to
find a threshold scale beyond which a physical model study could reliably
predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.

@@

Turbine performance is strongly dependent on the lift-to-drag ratio $l/d$ acting
on the blades, which is a function of the blades' angles of attack $\alpha$.
These angles of attack are a function of turbine tip speed ratio, induction
(slowing/turning of the free stream flow prior to reaching the turbine), and
turbine rotation or azimuthal angle $\theta$. Looking at static airfoil data, we
see that the static stall angle---the angle just beyond that at which $l/d$ is
maximum, characterized by flow separation near the leading edge---increases with
blade chord Reynolds number $Re_c$. This can be explained as the transition to a
turbulent boundary layer adjacent to the blade delaying separation.

@@

Static foil performance does not tell the whole story for a cross-flow turbine.
The azimuthal, and therefore temporal variation of $\alpha$ in a cross-flow
turbine implies the occurrence of dynamic stall at tip speed ratios at and below
those of maximum rotor torque\cite{Para2002}. We then must understand the
effects of Reynolds number on the dynamic stall process.
